---
title: "Titanicデータ確認"
date: "`r Sys.Date()`"
author: name
output:
  rmdformats::readthedown:
  highlight: kate
  code_folding: hide
  self_contained: true
  thumbnails: false
  lightbox: false
  md_extensions: -ascii_identifiers
  css: styles_customized.css
---
  
```{r knitr_init, echo=FALSE, results="asis", cache=FALSE}
## Global options
options(max.print = "75")
opts_chunk$set(echo = FALSE,
               cache = FALSE,
               prompt = FALSE,
               tidy = FALSE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 75)
```


# set dataset filename as list
```{r, echo=T}
if(T){
  lstInputFileNmList <- list()
  lstInputFileNmList[["train"]] <- "train.csv"
  lstInputFileNmList[["test"]] <- "test.csv"
  lstInputFileNmList[["submit"]] <- "gender_submission.csv"
}
```


# csvデータ読込み (read.csv)
```{r, echo=T}
inputFileName <- lstInputFileNmList[["train"]]
inputFilePath <- paste(inputDir, inputFileName, sep="")
datTrain <- read.csv(inputFilePath, header=T, stringsAsFactors=F)
```

# 対数変換
```{r, echo=T}
datTrain$Age_log <- log(1+abs(datTrain$Age))
datTrain$Fare_log <- log(1+abs(datTrain$Fare))
```

# データの次元 (dim)
```{r, echo=T}
dim(datTrain)
```


# データのレコード数 (nrow)
```{r, echo=T}
nrow(datTrain)
```


# データのカラム数 (ncol)
```{r, echo=T}
ncol(datTrain)
```


# カラム名 (colnames)
```{r, echo=T}
colnames(datTrain)
```


# カラム名・データ型 (str)
```{r, echo=T}
str(datTrain)
```


# 学習用データ数 (train.csv)
```{r, echo=F}
nSample <- format(nrow(datTrain), big.mark=",")
forprint <- paste("nSample = ", nSample, sep="")
print(forprint, quote=F)
```


# 先頭データ (head 6rows)
```{r results="asis", echo=T}
knitr::kable(head(datTrain), format="pandoc", caption="")
```


# 後尾データ (tail 6rows)
```{r results="asis", echo=T}
knitr::kable(tail(datTrain), format="pandoc", caption="")
```


# サマリー
```{r results="asis", echo=T}
summary(datTrain)
```


# 集計(1軸)
```{r results="asis", echo=T}
tbl <- table(datTrain[,"Survived"], useNA="always")
knitr::kable(tbl, format = "pandoc", caption="")
```


```{r results="asis", echo=T}
tbl <- table(datTrain[,"Pclass"], useNA="always")
knitr::kable(tbl, format = "pandoc", caption="")
```


```{r results="asis", echo=T}
tbl <- table(datTrain[,"Sex"], useNA="always")
knitr::kable(tbl, format = "pandoc", caption="")
```


# quantile
```{r results="asis", echo=T}
quantile(datTrain[,"Age"], na.rm=T, probs=seq(0,1,0.05))
quantile(datTrain[,"Age"], na.rm=T, probs=seq(0.95,1,0.005))
```


# histogram (Age)
```{r results="asis", echo=T}
p <- ggplot(datTrain, aes(x=Age))
p <- p + geom_histogram(colour="black", fill="white")
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```

# histogram (Age_log)
```{r results="asis", echo=T}
p <- ggplot(datTrain, aes(x=Age_log))
p <- p + geom_histogram(colour="black", fill="white")
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```

# histogram (Fare)
```{r results="asis", echo=T}
p <- ggplot(datTrain, aes(x=Fare))
p <- p + geom_histogram(colour="black", fill="white")
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```

# histogram (Fare_log)
```{r results="asis", echo=T}
p <- ggplot(datTrain, aes(x=Fare_log))
p <- p + geom_histogram(colour="black", fill="white")
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```



# boxplot (Age by Sex)
```{r results="asis", echo=T}
p <- ggplot(datTrain, aes(x=Sex, y=Age, group=Sex))
p <- p + geom_boxplot(outlier.shape=NA, notch=F, coef=1.0)
p <- p + stat_summary(fun.y=mean, geom="point", shape=20, size=3, fill="white", show.legend=FALSE)
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```


# boxplot (Fare, by Pclass)
```{r results="asis", echo=T}
p <- ggplot(datTrain, aes(x=Pclass, y=Fare_log, group=Pclass))
#p <- p + geom_boxplot(outlier.shape=NA, notch=F, coef=1.0)
p <- p + geom_boxplot()
p <- p + stat_summary(fun.y=mean, geom="point", shape=20, size=3, fill="white", show.legend=FALSE)
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```


# boxplot (Fare_log>2.0, by Pclass)
```{r results="asis", echo=T}
fillFlg_eff <- datTrain[,"Fare_log"]>2.0
datTrain_eff <- datTrain[fillFlg_eff,]

p <- ggplot(datTrain_eff, aes(x=Pclass, y=Fare_log, group=Pclass))
#p <- p + geom_boxplot(outlier.shape=NA, notch=F, coef=1.0)
p <- p + geom_boxplot()
p <- p + stat_summary(fun.y=mean, geom="point", shape=20, size=3, fill="white", show.legend=FALSE)
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```


# boxplot (Age by Survived)
```{r results="asis", echo=T}
p <- ggplot(datTrain, aes(x=Survived, y=Age, group=Survived))
#p <- p + geom_boxplot(outlier.shape=NA, notch=F, coef=1.0)
p <- p + geom_boxplot()
p <- p + stat_summary(fun.y=mean, geom="point", shape=20, size=3, fill="white", show.legend=FALSE)
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```

# boxplot (Fare_log > 2.0 by Survived)
```{r results="asis", echo=T}
fillFlg_eff <- datTrain[,"Fare_log"]>2.0
datTrain_eff <- datTrain[fillFlg_eff,]

p <- ggplot(datTrain_eff, aes(x=Survived, y=Fare_log, group=Survived))
#p <- p + geom_boxplot(outlier.shape=NA, notch=F, coef=1.0)
p <- p + geom_boxplot()
p <- p + stat_summary(fun.y=mean, geom="point", shape=20, size=3, fill="white", show.legend=FALSE)
p <- p + theme(axis.text.x=element_text(size=14, face="bold"),
               axis.text.y=element_text(size=14, face="bold"))
plot(p)
```


# 相関 (correlation) : {"Age","Embarked"}
```{r results="asis", echo=T}
library(psych)
psych::pairs.panels(datTrain[,c("Survived","Age","Embarked")])
```


# 相関 (correlation) : {"Pclass","Fare","Sex"}
```{r results="asis", echo=T}
library(psych)
psych::pairs.panels(datTrain[,c("Survived","Pclass","Fare","Sex")])
```


# 相関 (correlation) : {"SibSp","Parch","Cabin"}
```{r results="asis", echo=T}
library(psych)
psych::pairs.panels(datTrain[,c("Survived","SibSp","Parch","Cabin")])
```


# 相関 (correlation) : {"Pclass","Cabin"}
```{r results="asis", echo=T}
library(psych)
psych::pairs.panels(datTrain[,c("Survived","Pclass","Cabin")])
```


